The first high-redshift Changing Look Quasars

### 2019-12-02 tex/CIV_CLQs.tex
another major update; manuscript looking good :-)

The ZTF is a new robotic time-domain sky survey capable of visiting
the entire visible sky north of -30 deg. declination every night. ZTF
observes the sky in the $g$, $r$, and $i$-bands at different cadences
depending on the scientific program and sky region
\citep{Bellm2019_ZTFSurveys, Graham2019_ZTF}. The ZTF 576 megapixel
camera with a 47 deg$^{2}$ field of view, installed on the Samuel
Oschin 48-inch Schmidt Telescope, can scan more than 3750 deg$^{2}$
per hour, to a 5$\sigma$ detection limit of 20.7 mag in the $r$-band
with a 30sec exposure during new moon \citep{Masci2019}.
\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
  {figures/J1205+3422_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
  {figures/J1638+2827_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
  {figures/J2228+2201_landscape_20191112.png}
  \vspace{-12pt}
  \caption[]{The three high-$z$ CLQ quasars; 
    J1205+3422 (top), 
    J1638+2827 (middle) and  
    J2228+2201 (bottom). 
The light curve data is present in the panels on the left hand side, with the 
spectral epoch observational timings indicated by vertical lines. 
The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
complex, the \civ\ line, and the \mgii line. 
  }
  \label{fig:civ_clqs}
\end{figure*}

@@

%% From Section 3.1; Place here to help with overall formatting of
%% the paper
\input{QSFit-results}

@@

In particular we use the Quasar Spectral Fitting (QSFit) software
package presented in \citet{Calderone2017}. This provides luminosity
estimates as well as width, velocity offset and equivalent width of 20
emission lines, including \civ, \ciii and \mgii.  We process and fit
all nine spectra using the lastest version (v1.3.0) of the QSFit
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
calculator}. The host galaxy and blended iron emission at rest-frame
optical wavelengths components are automatically disabled when they
can not be constrained by the available data, such as the case for all
our objects (we do not have infrared spectral data).  Power-law
continuum slopes, $\alpha$, where $f_{\lambda} \propto
\lambda^{\alpha}$, are also reported in these catalogues and from
QSFit.  We quote the most appropriate value given the emission line
wavelength.

@@

%% trim={<left> <lower> <right> <upper>}
\begin{figure}
  \centering
  \includegraphics[width=8.40cm, trim=0.37cm 0.3cm 0.0cm 0.2cm, clip]{figures/CIVregions.png}
    \vspace{-18pt}
  \caption{Observed spectra and best fit model in the region relevant
    to \civ\ emission line for the quasars considered here.}
  \label{fig:QSFit-CIV}
\end{figure}
\subsection{\civ\ Emission Line Evolution}
We analyzed the spectra of the three quasars, at all observational
epochs, using the QSFit spectral fitting package
\citep{Calderone2017}.  One advantage of using QSFit is that it allows
constraints on the slope and luminosity of the broad band continuum of
the source. The relevant estimated quantities, including continuum
luminosity and slope at rest-frame 1450\AA, \civ\ line luminosity,
FWHM and EW are given in Tabl;e~\ref{tab:QSFit-results}. All fits are
performed with $E(B-V) = 0$ and the best fit model in the region of
the \civ\ emission line are shown in Figure~\ref{fig:QSFit-CIV}.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_MBHvsREW_QSFit20K.png}
   \vspace{-12pt}
   \caption[]{The virial black hole masses of $\approx$20,000 $z>1.5$ quasars
     from QSFit catalogue \citep{Calderone2017} and the \civ\ Equivalent widths.
     Different quasars are given different colours: J1205+3422 purple; J1638+2827 green; J2228+2201 is blue.
     Different epochs different symbols: first epoch circles; second epoch squares; third epoch diamonds. 
   }
  \label{fig:CIV_MBHvsREW}
\end{figure}
\subsection{Virial Black Hole Masses}
The FWHM of broad lines is likely related to the mass of the
supermassive black hole powering the quasar phenomenon, which is
assumed to be constant on any human timescale.  Hence it is
instructive to check whether the virial product, which is the basic
quantity used to calculate the single epoch black hole mass estimate,
show any variation.

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191128.png}
  \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
    of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
    of \citet{Hamann2017}.
   Symbols as in Fig.~\ref{fig:CIV_MBHvsREW}.}
  \label{fig:REWvsFWHM}
\end{figure}
\subsection{Quantified Temporal Evolution of \civ\ Emission}
Figure~\ref{fig:REWvsFWHM} shows the rest Equivalent Width (REW)
versus the Full Width Half Maximum (FWHM) of the \civ\ emission line
in the BOSS DR12 quasar sample using the catalogue of
\citet{Hamann2017}.

@@

\begin{table*}
  \begin{tabular}{l l  ll ll cc r}
    \hline
    \hline
    \multirow{ 2}{*}{Object}  & \multirow{ 2}{*}{MJD} & \multirow{ 2}{*}{$M_i$} &  \multirow{ 2}{*}{$L_{\rm bol}$}  & \multicolumn{2}{c}{$M_{\rm BH}$}     & \multicolumn{2}{c}{$\eta_{\rm Edd}$} &  Ref. \\
                              &                                   &                                      &                                                              & \mgii                  & \civ                    &  \mgii           &  \civ                       &        \\
    \hline
                              & 53498                         & -27.74                          & 47.216$\pm$0.004                            &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen11\\
    J1205+3422      & 58538                         &                                      &                                                            &                             &                             &                    &                               & \\
                              & 58693                         &                                     &                                                  &                             &                             &                    &                               &   \\
    \hline 
                              & 54553                          & -26.75                         & 46.166$\pm$0.04                    & 9.03$\pm$0.37    & 8.74$\pm$0.15  &  -0.964      & -0.677                      & Shen11\\
    J1638+2827                & 55832                         &  -26.40                         & 46.721$\pm$0.073                 & 9.34                      &  9.13                    &  -0.717     & -0.509                          & Kozl17\\
                              & 58583                          &                                      &                                                &                               &                            &                   &                                      &  \\
    \hline 
                              & 56189                          &  -25.46                         & 46.231$\pm$0.073                 &  9.45                     & 8.73                     &  -1.317   & -0.602                            & Kozl17\\
    J2228+2201       & 56960                          &                                       &                                                &                              &                               &                 &                                        & \\
                              & 58693                          &                                       &                                               &                               &                                &                &                   &  \\
     \hline
    \hline
  \end{tabular}
  \caption{Physical properties of the \civ\ CLQs. 
     $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude $K$-corrected to $z = 2$; Bolometric luminosity computed from the
        monochromatic luminosity at 1350\AA\ using the spectral fits and
        bolometric corrections (BC = 3.81) in \citet{Richards2006b}.
        Virial BH masses using calibrations of \citet{VestergaardPeterson2006}.
         $\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio computed using the virial BH mass.
        Shen11 is \citet{Shen2011}. 
        Kozl17 is \citet{Kozlowski2017}. }
\label{tab:Eddington_ratios} 
\end{table*}

@@

There is an anti-correlation between the emission-line REWs and
e.g. 1450\AA\ rest continuum luminosity, so that as the underlying UV
continuum luminosity increases, the EW decreses. 
Figure~\ref{fig:CIV_Baldwin} shows this for a sample (from the QSFit catalogue)
for 20,374 quasars.  The slope (not shown) is $\beta$ is $-0.1997$.
This is consistent with \citet{Kozlowski2017}, using their bolometric
luminosity gives a slope of $\beta=-0.251$ and in line with that from
\citet[][ $\beta=-0.23$]{Hamann2017}.

@@

@@

\begin{figure*}
  \centering
  \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/MJD_vs_Eddington_20191129.png}
  \vspace{-12pt}
  \caption[]{Eddington Ratios of the three \civ\ CLQs and M87.}
  \label{fig:Eddington_ratios}
\end{figure*}
\subsection{Eddington Ratios and State Changes} 
The broad UV and optical lines in quasars are most sensitive to the
extreme ultraviolet (EUV) part of the spectral energy distribution
(SED), with \civ\ (and indeed \heii and \nv) being at the higher
energy end of the EUV distribution.

@@

By comparing the observed correlations between the UV/optical-to-X-ray
spectral index ($\alpha_{\rm ox}$) and Eddington ratio in AGN to those
predicted from observations of X-ray binary outbursts,
\citet{Ruan2019a} find a remarkable similarity to accretion state transitions in prototypical
X-ray binary outbursts, including an inversion of this correlation at
a critical Eddington ratio of $\sim$10$^{-2}$ (i.e. at the same ratio
as motivated by \citet{NodaDone2018}).  These results suggest that the
structures of black hole accretion flows directly scale across a
factor of $\sim10^{8}$ in black hole mass and across different
accretion states. Using \citet{Ruan2019a} as a guide, there are potentially three accretion regimes: 
(1) a ``High/Soft State'' with $\eta_{\rm Edd} \gtrsim -1$; 
(1) a ``Low/Hard State'' with $-2 \lesssim \eta_{\rm Edd} \lesssim  -1$;
(1) a ``High/Soft State'' with $\eta_{\rm Edd} \lesssim -2$.
These are given as shaded regions in Figure~\ref{fig:Eddington_ratios}.

>>>>

The ZTF is a new robotic time-domain sky survey capable of visiting
the entire visible sky north of -30 deg. declination every night. ZTF
observes the sky in the $g$, $r$, and $i$-bands at different cadences
depending on the scientific program and sky region
\citep{Bellm2019_ZTFSurveys, Graham2019_ZTF}. The ZTF 576 megapixel
camera with a 47 deg$^{2}$ field of view, installed on the Samuel
Oschin 48-inch Schmidt Telescope, can scan more than 3750 deg$^{2}$
per hour, to a 5$\sigma$ detection limit of 20.7 mag in the $r$-band
with a 30sec exposure during new moon \citep{Masci2019}.
\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
  {figures/J1205+3422_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
  {figures/J1638+2827_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
  {figures/J2228+2201_landscape_20191112.png}
  \vspace{-12pt}
  \caption[]{The three high-$z$ CLQ quasars; 
    J1205+3422 (top), 
    J1638+2827 (middle) and  
    J2228+2201 (bottom). 
    The light curve data is present in the panels on the left hand side, with the 
    spectral epoch observational timings indicated by vertical lines. 
    The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
    complex, the \civ\ line, and the \mgii line.}
  \label{fig:civ_clqs}
\end{figure*}

@@

%% From Section 3.1; Placed here to help with overall formatting of the paper
\input{QSFit-results}

@@

In particular we use the Quasar Spectral Fitting (QSFit) software
package presented in \citet{Calderone2017}. This provides luminosity
estimates as well as width, velocity offset and equivalent width of 20
emission lines, including \civ, \ciii and \mgii.  We process and fit
all nine spectra using the lastest version (v1.3.0) of the QSFit
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
calculator}. The host galaxy and blended iron emission at rest-frame
optical wavelengths components are automatically disabled when they
can not be constrained by the available data, such as the case for all
our objects (we do not have infrared spectral data).  Power-law
continuum slopes, $\alpha$, where $f_{\lambda} \propto
\lambda^{\alpha}$, are also reported in these catalogues and from
QSFit.

@@

%% trim={<left> <lower> <right> <upper>}
\begin{figure}
  \centering
  \includegraphics[width=8.40cm, trim=0.37cm 0.3cm 0.0cm 0.2cm, clip]{figures/CIVregions.png}
    \vspace{-18pt}
  \caption{Observed spectra and best fit model in the region relevant
    to \civ\ emission line for the quasars considered here.
    The solid blue line is the Lorentzian profile fit the to the \civ\ emission line.
    The long-dashed red line is the continuum fit, with the solid orange
    line giving the overall fit. The short-dashed vertical lines gives the
    rest wavelengths of the \civ\ doublet. }
  \label{fig:QSFit-CIV}
\end{figure}
\subsection{\civ\ Emission Line Evolution}
We analyzed the spectra of the three quasars, at all observational
epochs, using the QSFit spectral fitting package
\citep{Calderone2017}.  One advantage of using QSFit is that it allows
constraints on the slope and luminosity of the broad band continuum of
the source. The relevant estimated quantities, including continuum
luminosity and slope at rest-frame 1450\AA, \civ\ line luminosity,
FWHM and EW are given in Tabl;e~\ref{tab:QSFit-results}. All fits are
performed with $E(B-V) = 0$ and the best fit model in the region of
the \civ\ emission line are shown in Figure~\ref{fig:QSFit-CIV}.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_MBHvsREW_QSFit20K.png}
   \vspace{-12pt}
   \caption[]{The virial black hole masses of $\approx$20,000 $z>1.5$ quasars
     from QSFit catalogue \citep{Calderone2017} and the \civ\ Equivalent widths.
     Different quasars are given different colours: J1205+3422 purple; J1638+2827 green; J2228+2201 is blue.
     Different epochs different symbols: first epoch circles; second epoch squares; third epoch diamonds. 
   }
  \label{fig:CIV_MBHvsREW}
\end{figure}
\subsection{Virial Black Hole Masses}\label{sec:BH_masses} 
The FWHM of broad lines is likely related to the mass of the
supermassive black hole powering the quasar phenomenon, which is
assumed to be constant on any human timescale.  Hence it is
instructive to check whether the virial product, which is the basic
quantity used to calculate the single epoch black hole mass estimate,
show any variation.

@@

\citet{Shen2011} reports Virial BH mass based on \mgii and \civ\ as
$\log (M/M_{\rm BH}) = 9.55\pm0.05$ and $\log(M/M_{\rm BH}) =
9.49\pm0.04$, respectively. We thus use the mean of these five values
(three from our three epochs and the two \citet{Shen2011} values) to
establish a working mean SMBH mass of $\log (M_{\rm BM, vir}/M_{\odot})
= 9.726$ for J1205+3422.  J1638+2827 also has two virial mass
measurments from Shen2011, but also has two measurements from
\citet{Kozlowski2017} (again using \civ and \mgii). The mean mass
measurement for J1638+2827 here is $\log(M_{\rm BM, vir}/M_{\odot} =
9.091$. For J2228+2201 there are two \citet{Kozlowski2017}, leading to
a mean mass of $\log(M_{\rm BM, vir}/M_{\odot} = 9.366$. We use these
mean SMBH masses when calculating the Eddington ratios.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191128.png}
  \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
    of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
    of \citet{Hamann2017}.
   Symbols as in Fig.~\ref{fig:CIV_MBHvsREW}.}
  \label{fig:REWvsFWHM}
\end{figure}
\subsection{Quantified Temporal Evolution of \civ\ Emission}
Quasars with interesting physical properties, such as extreme
outflows, can be selected using EW and FWHM measurements, \citep[e.g.,
the ``Extremely Red Quasars'' (ERQs)][]{Ross2015, Zakamska2016,
Hamann2017, Zakamska2019}. Figure~\ref{fig:REWvsFWHM} shows the rest
Equivalent Width (REW) versus the Full Width Half Maximum (FWHM) of
the \civ\ emission line in the BOSS DR12 quasar sample using the
catalogue of \citet{Hamann2017}.

@@

\begin{table}
  \centering
  \begin{tabular}{l l l r}
    \hline
    \hline
    Object           & MJD      & $L_{\rm bol}$    &  $\eta_{\rm Edd}$  \\
    \hline
                         & 53498    & 47.216           &  -0.610                  \\
    J1205+3422 & 58538    &  46.567          &  -1.259  \\                        %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
                         & 58693     &  46.070         &  -1.756 \\
    \hline 
                          & 54553   & 46.166    & -1.025 \\
    J1638+2827  & 55832   & 45.981    & -1.210  \\                                            %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
                          & 58583   & 46.504   & -0.687       \\
    \hline 
                          & 56189   & 46.231   &  -1.235 \\
    J2228+2201   & 56960    & 47.342   & -0.124 \\                                             %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
                          & 58693   & 46.826     &  -0.640 \\
    \hline
    \hline
  \end{tabular}
  \caption{
    Bolometric luminosities are given in either \citet{Shen2011} or 
    \citet{Kozlowski2017} for the three CLQs. We scale these 
    values using our measured $\nu L_{\nu}$ continuum luminosity values.
    From Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BM, vir}/M_{\odot}) = 9.726$ for J1205+3422,
    $\log(M_{\rm BM, vir}/M_{\odot} = 9.091$ for  J1638+2827 
    and $\log(M_{\rm BM, vir}/M_{\odot} = 9.366$ for J2228+2201. 
    The Eddington Luminosity is 
    $L_{\rm Edd} = 1.26\times10^{38} (M/M_{\odot})$ erg s$^{-1}$ and
    %%  6.70456406676162      e+47  for J12
    %%  1.5537120898684228  e+47  for J16
    %%  2.9266483634099527  e+47 for J22
   $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
\label{tab:Eddington_ratios} 
\end{table}

@@

There is an anti-correlation between the emission-line REWs and
e.g. 1450\AA\ rest continuum luminosity, so that as the underlying UV
continuum luminosity increases, the EW decreases. 
Figure~\ref{fig:CIV_Baldwin} shows this for a sample (from the QSFit catalogue)
for 20,374 quasars.  The slope (not shown) is $\beta$ is $-0.1997$.
This is consistent with \citet{Kozlowski2017}, using their bolometric
luminosity gives a slope of $\beta=-0.251$ and in line with that from
\citet[][ $\beta=-0.23$]{Hamann2017}.

@@

\citet{Graham2019} report the largest number of H$\beta$ CSQs with 111
sources being identified. \citet{Graham2019} find that this population
of extreme varying quasars is associated with {\it changes} in the
Eddington ratio, (rather than just the magnitude of the Eddington
ratio itself) and the timescales imply cooling/heating fronts
propagating through the disk.\\
{\bf NPR to finish this off} \\

@@

\begin{figure*}
  \centering
  \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/MJD_vs_Eddington_20191202.png}
  \vspace{-12pt}
  \caption[]{Eddington Ratios of the three \civ\ CLQs.
    Grayscale gives the Eddington Ratio ranges for the SDSS
    \citep[from ][]{Shen2011} and the BOSS \citep[from ][]{Kozlowski2017)} 
    catalogues.
    Symbols as in Fig.~\ref{fig:CIV_MBHvsREW}.
    The red region ($L / L_{\rm Edd} \approx 0.02\pm0.01$;  $\eta =-1.7\pm0.13$) is
    the transition accretion rate suggested by \citet{NodaDone2018}.
    A ``High/Soft State'' with $\eta_{\rm Edd} \geq -1$ and a
    a ``Low/Hard State'' with $\eta_{\rm Edd} \leq -2$ are indicated 
    with dahsed lines and arrows. 
  }
  \label{fig:Eddington_ratios}
\end{figure*}
\subsection{Eddington Ratios and State Changes} 
The broad UV and optical lines in quasars are most sensitive to the
extreme ultraviolet (EUV) part of the spectral energy distribution
(SED), with \civ\ (and indeed \heii and \nv) being at the higher
energy end of the EUV distribution.

@@

By comparing the observed correlations between the UV/optical-to-X-ray
spectral index ($\alpha_{\rm ox}$) and Eddington ratio in AGN to those
predicted from observations of X-ray binary outbursts,
\citet{Ruan2019a} find a remarkable similarity to accretion state transitions in prototypical
X-ray binary outbursts, including an inversion of this correlation at
a critical Eddington ratio of $\sim$10$^{-2}$ (i.e. at the same ratio
as motivated by \citet{NodaDone2018}).  These results suggest that the
structures of black hole accretion flows directly scale across a
factor of $\sim10^{8}$ in black hole mass and across different
accretion states. Using \citet{Ruan2019a} as a guide, there are potentially three accretion regimes: 
(1) a ``High/Soft State'' with $\eta_{\rm Edd} \gtrsim -1$; 
(1) a ``Low/Hard State'' with $-2 \lesssim \eta_{\rm Edd} \lesssim  -1$;
(1) a ``Low/Hard State'' with $\eta_{\rm Edd} \lesssim -2$.
These are given as shaded regions in Figure~\ref{fig:Eddington_ratios}.
